---
title: "Comparison of RF implementations with microbenchmark"
author: "Robin Genuer"
date: "15 july 2019"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_float: yes
---

```{r, message=FALSE}
library(microbenchmark)
library(ggplot2)
```

```{r, echo=FALSE}
resFiles <- list.files("outputs/")
for (fileName in resFiles) {
  load(paste0("outputs/", fileName))
}
```

```{r}
mbplot <- function(res) {
  resDF <- as.data.frame(res)
  ggres <- ggplot(resDF, aes(expr, time)) + theme_bw() + ylab("time (log scale)") +
    theme(panel.grid.minor = element_blank(), panel.grid.major = element_blank()) +
    geom_boxplot(aes(fill = expr))# + scale_y_continuous(trans = "log10")
}
```


# `toys` data: high-dimensional case

## $n=100$, $p=200$

```{r}
data(toys, package = "VSURF")
dim(toys$x)
str(toys$y)
toysData <- data.frame(toys$x, y = toys$y)
mtryToys <- floor(ncol(toys$x)/3)
```

```{r, eval=FALSE}
mbToys <- microbenchmark::microbenchmark(
  randomForest::randomForest(y ~ ., toysData, mtry = mtryToys),
  randomForest::randomForest(toys$x, toys$y, mtry = mtryToys),
  ranger::ranger(y ~ ., toysData, mtry = mtryToys, num.threads = 1),
  Rborist::Rborist(toys$x, toys$y, predFixed = mtryToys, minInfo = 0, nThread = 1),
  times = 25)
levels(mbToys$expr) <- c("RF formula", "RF", "ranger", "Rborist")
```

```{r}
mbToys
save(mbToys, file = "outputs/mbToys.Rdata")
# plotToys <- mbplot(mbToys) + scale_fill_manual(values = viridis::viridis(4))
# plotToys
```


### With variable importance computation

```{r, eval=FALSE}
mbToys <- microbenchmark::microbenchmark(
  randomForest::randomForest(y ~ ., toysData, mtry = mtryToys, importance = TRUE),
  randomForest::randomForest(toys$x, toys$y, mtry = mtryToys, importance = TRUE),
  ranger::ranger(y ~ ., toysData, mtry = mtryToys, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbToys$expr) <- c("RF formula", "RF", "ranger")
```

```{r}
mbToysImp
save(mbToysImp, file = "outputs/mbToysImp.Rdata")
# plotToysImp <- mbplot(mbToysImp) + scale_fill_manual(values = viridis::viridis(4)[1:3])
# plotToysImp
```


```{r}
mbToys$VI <- "no VI"
mbToysImp$VI <- "VI"
mbToysBoth <- rbind(mbToys, mbToysImp)
toysMBplot <- mbplot(mbToysBoth)
toysMBplot <- toysMBplot + facet_wrap(~VI) +
    scale_fill_manual(values = viridis::viridis(4))
toysMBplot
```


## $n=100$, $p=2 000$

```{r, echo=FALSE}
addVarNoise <- function(x, nbVarNoise){
  nbObs <- nrow(x)
  nbVar <- ncol(x)
  addNoise <- matrix(rnorm(nbObs*nbVarNoise, 0, 20), nrow = nbObs)
  xc <- cbind(x, addNoise)
  colnames(xc) <- paste0("X", 1:(nbVar + nbVarNoise))
  
  return(xc)
}

ajoutVarCor2grp <- function(x, j, k, d, rho = 1.0324){
  if (d == 0) {
    return(x)
  }
  else {
    sigma=0.5
    n=nrow(x)
    z=matrix(0,n,d)
    w=matrix(0,n,d)
    
    for (i in 1:d){
      u=matrix(0,n,1)
      u[,1]=rnorm(n,0,1)
      z[,i]=x[,j]*rho+sigma*u
      z[,i]=(z[,i]-mean(z[,i]))/sqrt(var(z[,i]))
      w[,i]=x[,k]*rho+sigma*u
      w[,i]=(w[,i]-mean(w[,i]))/sqrt(var(w[,i]))
    }
    
    p=ncol(x)
    xc=matrix(0,n,p+2*d)
    
    for (i in 1:d){
      xc[,6+i]=z[,i]
      xc[,6+d+i]=w[,i]
    }
    
    for (i in 1:6){
      xc[,i]=x[,i]
    }
    
    for (i in 7:p){
      xc[,2*d+i]=x[,i]
    }
    
    return(xc)
  }
}
```

```{r}
bigToys <- ajoutVarCor2grp(toys$x, j = 3, k = 6, d = 30)
bigToys <- addVarNoise(bigToys, 2000 - ncol(bigToys))
dim(bigToys)
bigToysData <- data.frame(bigToys, y = toys$y)
mtryBigToys <- floor(ncol(bigToys)/10)
```

```{r, eval=FALSE}
mbbigToys <- microbenchmark::microbenchmark(
  randomForest::randomForest(y ~ ., bigToysData, mtry = mtryBigToys),
  randomForest::randomForest(bigToys, toys$y, mtry = mtryBigToys),
  ranger::ranger(y ~ ., bigToysData, mtry = mtryBigToys, num.threads = 1),
  Rborist::Rborist(bigToys, toys$y, predFixed = mtryBigToys, minInfo = 0, nThread = 1),
  times = 25)
levels(mbToys$expr) <- c("RF formula", "RF", "ranger", "Rborist")
```

```{r}
mbbigToys
save(mbbigToys, file = "outputs/mbbigToys.Rdata")
# plotbigToys <- mbplot(mbbigToys) + scale_fill_manual(values = viridis::viridis(4)[2:4])
# plotbigToys
```


### With variable importance computation

```{r, eval=FALSE}
mbbigToysImp <- microbenchmark::microbenchmark(
  randomForest::randomForest(y ~ ., bigToysData, mtry = mtryBigToys, importance = TRUE),
  randomForest::randomForest(bigToys, toys$y, mtry = mtryBigToys, importance = TRUE),
  ranger::ranger(y ~ ., bigToysData, mtry = mtryBigToys, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbbigToysImp$expr) <- c("RF formula", "RF", "ranger")
```

```{r}
mbbigToysImp
save(mbbigToysImp, file = "outputs/mbbigToysImp.Rdata")
# plotbigToysImp <- mbplot(mbbigToysImp) + scale_fill_manual(values = viridis::viridis(4)[1:3])
# plotbigToysImp
```

```{r}
mbbigToys$VI <- "no VI"
mbbigToysImp$VI <- "VI"
mbbigToysBoth <- rbind(mbbigToys, mbbigToysImp)
bigtoysMBplot <- mbplot(mbbigToysBoth)
bigtoysMBplot <- bigtoysMBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[1:3])
bigtoysMBplot
```



## $n=100$, $p=5 000$

```{r}
BIGToys <- ajoutVarCor2grp(toys$x, j = 3, k = 6, d = 300)
BIGToys <- addVarNoise(BIGToys, 5000 - ncol(BIGToys))
dim(BIGToys)
BIGToysData <- data.frame(BIGToys, y = toys$y)
mtryBIGToys <- floor(ncol(BIGToys)/10)
```

```{r, eval=FALSE}
mbBIGToys <- microbenchmark::microbenchmark(
  randomForest::randomForest(BIGToys, toys$y, mtry = mtryBIGToys),
  ranger::ranger(y ~ ., BIGToysData, mtry = mtryBIGToys, num.threads = 1),
  times = 25)
levels(mbBIGToys$expr) <- c("RF", "ranger")
```

```{r}
mbBIGToys
save(mbBIGToys, file = "outputs/mbBIGToys.Rdata")
# plotBIGToys <- mbplot(mbBIGToys) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotBIGToys
```


### With variable importance computation

```{r, eval=FALSE}
mbBIGToys <- microbenchmark::microbenchmark(
  randomForest::randomForest(BIGToys, toys$y, mtry = mtryBIGToys, importance = TRUE),
  ranger::ranger(y ~ ., BIGToysData, mtry = mtryBIGToys, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbBIGToys$expr) <- c("RF", "ranger")
```

```{r}
mbBIGToysImp
save(mbBIGToysImp, file = "outputs/mbBIGToysImp.Rdata")
# plotBIGToysImp <- mbplot(mbBIGToysImp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotBIGToysImp
```


```{r}
mbBIGToys$VI <- "no VI"
mbBIGToysImp$VI <- "VI"
mbBIGToysBoth <- rbind(mbBIGToys, mbBIGToysImp)
BIGtoysMBplot <- mbplot(mbBIGToysBoth)
BIGtoysMBplot <- BIGtoysMBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[2:3])
BIGtoysMBplot
```



## $n=100$, $p=10 000$

```{r}
BIGToys2 <- ajoutVarCor2grp(toys$x, j = 3, k = 6, d = 300)
BIGToys2 <- addVarNoise(BIGToys2, 10000 - ncol(BIGToys2))
dim(BIGToys2)
BIGToys2Data <- data.frame(BIGToys2, y = toys$y)
mtryBIGToys2 <- floor(ncol(BIGToys2)/10)

```

```{r, eval=FALSE}
mbBIGToys2 <- microbenchmark::microbenchmark(
  randomForest::randomForest(BIGToys, toys$y, mtry = mtryBIGToys),
  ranger::ranger(y ~ ., BIGToysData, mtry = mtryBIGToys, num.threads = 1),
  times = 25)
levels(mbBIGToys2$expr) <- c("RF", "ranger")
```

```{r}
mbBIGToys2
save(mbBIGToys2, file = "outputs/mbBIGToys2.Rdata")
# plotBIGToys2 <- mbplot(mbBIGToys2) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotBIGToys2
```


### With variable importance computation

```{r, eval=FALSE}
mbBIGToys2Imp <- microbenchmark::microbenchmark(
  randomForest::randomForest(BIGToys, toys$y, mtry = mtryBIGToys, importance = TRUE),
  ranger::ranger(y ~ ., BIGToysData, mtry = mtryBIGToys, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbBIGToys2Imp$expr) <- c("RF", "ranger")
```

```{r}
mbBIGToys2Imp
save(mbBIGToys2Imp, file = "outputs/mbBIGToys2Imp.Rdata")
# plotBIGToys2Imp <- mbplot(mbBIGToys2Imp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotBIGToys2Imp
```


```{r}
mbBIGToys2$VI <- "no VI"
mbBIGToys2Imp$VI <- "VI"
mbBIGToys2Both <- rbind(mbBIGToys2, mbBIGToys2Imp)
BIGToys2MBplot <- mbplot(mbBIGToys2Both)
BIGToys2MBplot <- BIGToys2MBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[2:3])
BIGToys2MBplot
```




# `vac18` data $n=42$, $p=1000$

```{r}
data("vac18", package = "mixOmics")
geneExpr <- vac18$genes
dim(geneExpr)
stimu <- vac18$stimulation
str(stimu)
VAC18 <- data.frame(geneExpr, stimu)
mtryVac18 <- floor(ncol(geneExpr)/3)
```

```{r, eval=FALSE}
mbVac18 <- microbenchmark::microbenchmark(
  randomForest::randomForest(stimu ~ ., VAC18, mtry = mtryVac18),
  randomForest::randomForest(geneExpr, stimu, mtry = mtryVac18),
  ranger::ranger(stimu ~ ., VAC18, mtry = mtryVac18, num.threads = 1),
  Rborist::Rborist(geneExpr, stimu, predFixed = mtryVac18, minInfo = 0, nThread = 1),
  times = 25)
levels(mbVac18$expr) <- c("RF formula", "RF", "ranger", "Rborist")
```

```{r}
mbVac18
save(mbVac18, file = "outputs/mbVac18.Rdata")
# plotVac18 <- mbplot(mbVac18) + scale_fill_manual(values = viridis::viridis(4))
# plotVac18
```

## With variable importance computation

```{r, eval=FALSE}
mbVac18Imp <- microbenchmark::microbenchmark(
  randomForest::randomForest(stimu ~ ., VAC18, mtry = mtryVac18, importance = TRUE),
  randomForest::randomForest(geneExpr, stimu, mtry = mtryVac18, importance = TRUE),
  ranger::ranger(stimu ~ ., VAC18, mtry = mtryVac18, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbVac18Imp$expr) <- c("RF formula", "RF", "ranger")
```

```{r}
mbVac18Imp
save(mbVac18Imp, file = "outputs/mbVac18Imp.Rdata")
# plotVac18Imp <- mbplot(mbVac18Imp) + scale_fill_manual(values = viridis::viridis(4)[1:3])
# plotVac18Imp
```


```{r}
mbVac18$VI <- "no VI"
mbVac18Imp$VI <- "VI"
mbVac18Both <- rbind(mbVac18, mbVac18Imp)
Vac18MBplot <- mbplot(mbVac18Both)
Vac18MBplot <- Vac18MBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4))
Vac18MBplot
```


# `spam` data

## $n=4601$, $p=57$

```{r}
data("spam", package = "kernlab")
nvarSpam <- ncol(spam) - 1
Xspam <- spam[, -ncol(spam)]
Yspam <- spam$type
dim(Xspam)
str(Yspam)
mtrySpam <- floor(sqrt(nvarSpam))
```

```{r, eval=FALSE}
mbSpam <- microbenchmark(
  randomForest::randomForest(type ~ ., spam, mtry = mtrySpam),
  ranger::ranger(type ~ ., spam, mtry = mtrySpam, num.threads = 1),
  Rborist::Rborist(Xspam, Yspam, predFixed = mtrySpam, minInfo = 0, nThread = 1),
  times = 25)
levels(mbSpam$expr) <- c("RF", "ranger", "Rborist")
```

```{r}
mbSpam
save(mbSpam, file = "outputs/mbSpam.Rdata")
# plotSpam <- mbplot(mbSpam) + scale_fill_manual(values = viridis::viridis(4)[2:4])
# plotSpam
```

### With variable importance computation

```{r, eval=FALSE}
mbSpamImp <- microbenchmark(
  randomForest::randomForest(type ~ ., spam, mtry = mtrySpam, importance = TRUE),
  ranger::ranger(type ~ ., spam, mtry = mtrySpam, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbSpamImp$expr) <- c("RF", "ranger")
```

```{r}
mbSpamImp
save(mbSpamImp, file = "outputs/mbSpamImp.Rdata")
# plotSpamImp <- mbplot(mbSpamImp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotSpamImp
```

```{r}
mbSpam$VI <- "no VI"
mbSpamImp$VI <- "VI"
mbSpamBoth <- rbind(mbSpam, mbSpamImp)
SpamMBplot <- mbplot(mbSpamBoth)
SpamMBplot <- SpamMBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[2:4])
SpamMBplot
```


## $n=4601$, $p=1$

```{r}
spamSmall <- spam[, c("charExclamation", "type")]
str(spamSmall)
XspamSmall <- spamSmall["charExclamation"]
YspamSmall <- spamSmall$type
```

```{r, eval=FALSE}
mbSpamSmall <- microbenchmark(
  randomForest::randomForest(type ~ ., spamSmall, mtry = 1),
  ranger::ranger(type ~ ., spamSmall, mtry = 1, num.threads = 1),
  Rborist::Rborist(XspamSmall, YspamSmall, predFixed = 1, minInfo = 0, nThread = 1),
  times = 25)
levels(mbSpamSmall$expr) <- c("RF", "ranger", "Rborist")
```

```{r}
mbSpamSmall
save(mbSpamSmall, file = "outputs/mbSpamSmall.Rdata")
# plotSpamSmall <- mbplot(mbSpamSmall) + scale_fill_manual(values = viridis::viridis(4)[2:4])
# plotSpamSmall
```

### With variable importance computation

```{r, eval=FALSE}
mbSpamSmallImp <- microbenchmark(
  randomForest::randomForest(type ~ ., spamSmall, mtry = 1, importance = TRUE),
  ranger::ranger(type ~ ., spamSmall, mtry = 1, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbSpamSmallImp$expr) <- c("RF", "ranger")
```


```{r}
mbSpamSmallImp
save(mbSpamSmallImp, file = "outputs/mbSpamSmallImp.Rdata")
# plotSpamSmallImp <- mbplot(mbSpamSmallImp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotSpamSmallImp
```

```{r}
mbSpamSmall$VI <- "no VI"
mbSpamSmallImp$VI <- "VI"
mbSpamSmallBoth <- rbind(mbSpamSmall, mbSpamSmallImp)
SpamSmallMBplot <- mbplot(mbSpamSmallBoth)
SpamSmallMBplot <- SpamSmallMBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[2:4])
SpamSmallMBplot
```



# `toys` data: big data case

```{r}
simu_toys <- function(n, p, q = 0.7) {
  y <- 2 * rbinom(n, 1, 0.5) - 1
  x <- matrix(NA, n, p)
  r <- floor(q*n)
  z <- 1:r
  for (i in 1:3) {
    x[z, i] <- y[z] * rnorm(r, i, 1)
    x[-z, i] <- y[-z] * rnorm(n - r, 0, 1)
  }
  for (i in 4:6) {
    x[z, i] <- y[z] * rnorm(r, 0, 1)
    x[-z, i] <- y[-z] * rnorm(n - r, i - 3, 1)
  }
  x[, 7:p] <- rnorm(n*(p - 6), 0, 20)
  x <- scale(x)
  y <- as.factor(y)
  output <- data.frame('x' = x, 'y' = y)
}
```


## $n = 1000, p = 10$

```{r}
ncores <- 4
set.seed(768895) 
allseeds <- round(runif(ncores, 1e5, 1e6))

alldata <- parallel::mclapply(1:ncores, function(ind) {
  set.seed(allseeds[ind])
  simu_toys(n = 1000 / ncores, p = 10)
}, mc.cores=ncores)

TallToys <- do.call("rbind", alldata)
dim(TallToys)
save(TallToys, file = "data/TallToys.Rdata")

mtryTallToys <- floor(sqrt(ncol(TallToys) - 1))
```

```{r, eval=FALSE}
mbTallToys <- microbenchmark(
  randomForest::randomForest(y ~ ., TallToys, mtry = mtryTallToys),
  ranger::ranger(y ~ ., TallToys, mtry = mtryTallToys, num.threads = 1),
  Rborist::Rborist(subset(TallToys, select = -y), TallToys$y, predFixed = mtryTallToys, minInfo = 0, nThread = 1),
  times = 25)
levels(mbTallToys$expr) <- c("RF", "ranger", "Rborist")
```

```{r}
mbTallToys
save(mbTallToys, file = "outputs/mbTallToys.Rdata")
# plotTallToys <- mbplot(mbTallToys) + scale_fill_manual(values = viridis::viridis(4)[2:4])
# plotTallToys
```

### With variable importance computation

```{r, eval=FALSE}
mbTallToysImp <- microbenchmark(
  randomForest::randomForest(y ~ ., TallToys, mtry = mtryTallToys, importance = TRUE),
  ranger::ranger(y ~ ., TallToys, mtry = mtryTallToys, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbTallToysImp$expr) <- c("RF", "ranger")
```

```{r}
mbTallToysImp
save(mbTallToysImp, file = "outputs/mbTallToysImp.Rdata")
# plotTallToysImp <- mbplot(mbTallToysImp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotTallToysImp
```

```{r}
mbTallToys$VI <- "no VI"
mbTallToysImp$VI <- "VI"
mbTallToysBoth <- rbind(mbTallToys, mbTallToysImp)
TallToysMBplot <- mbplot(mbTallToysBoth)
TallToysMBplot <- TallToysMBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[2:4])
TallToysMBplot
```


## $n = 10000, p = 10$

```{r}
set.seed(768895) 
allseeds <- round(runif(ncores, 1e5, 1e6))

alldata <- parallel::mclapply(1:ncores, function(ind) {
  set.seed(allseeds[ind])
  simu_toys(n = 10000 / ncores, p = 10)
}, mc.cores=ncores)

TALLToys <- do.call("rbind", alldata)
dim(TALLToys)
# save(TallToys, file = "data/TallToys.Rdata")

mtryTALLToys <- floor(sqrt(ncol(TALLToys) - 1))
```

```{r, eval=FALSE}
mbTALLToys <- microbenchmark(
  randomForest::randomForest(y ~ ., TALLToys, mtry = mtryTALLToys),
  ranger::ranger(y ~ ., TALLToys, mtry = mtryTALLToys, num.threads = 1),
  Rborist::Rborist(subset(TALLToys, select = -y), TALLToys$y, predFixed = mtryTALLToys, minInfo = 0, nThread = 1),
  times = 25)
levels(mbTALLToys$expr) <- c("RF", "ranger", "Rborist")
```

```{r}
mbTALLToys
save(mbTALLToys, file = "outputs/mbTALLToys.Rdata")
# plotTALLToys <- mbplot(mbTALLToys) + scale_fill_manual(values = viridis::viridis(4)[2:4])
# plotTALLToys
```

### With variable importance computation

```{r, eval=FALSE}
mbTALLToysImp <- microbenchmark(
  randomForest::randomForest(y ~ ., TALLToys, mtry = mtryTALLToys, importance = TRUE),
  ranger::ranger(y ~ ., TALLToys, mtry = mtryTALLToys, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbTALLToysImp$expr) <- c("RF", "ranger")
```

```{r}
mbTALLToysImp
save(mbTALLToysImp, file = "outputs/mbTALLToysImp.Rdata")
# plotTALLToysImp <- mbplot(mbTALLToysImp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotTALLToysImp
```


```{r}
mbTALLToys$VI <- "no VI"
mbTALLToysImp$VI <- "VI"
mbTALLToysBoth <- rbind(mbTALLToys, mbTALLToysImp)
TALLToysMBplot <- mbplot(mbTALLToysBoth)
TALLToysMBplot <- TALLToysMBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[2:4])
TALLToysMBplot
```


## $n = 10000, p = 1$

```{r}
TALLthinToys <- TALLToys
TALLthinToys$x <- TALLToys$x[, 1]
```

```{r, eval=FALSE}
mbTALLthinToys <- microbenchmark(
  randomForest::randomForest(y ~ ., TALLthinToys, mtry = 1),
  ranger::ranger(y ~ ., TALLthinToys, mtry = 1, num.threads = 1),
  # Rborist::Rborist(subset(TALLthinToys, select = -y), TALLthinToys$y, predFixed = 1, minInfo = 0, nThread = 1),
  times = 25)
levels(mbTALLthinToys$expr) <- c("RF", "ranger", "Rborist")
```

```{r}
mbTALLthinToys
save(mbTALLthinToys, file = "outputs/mbTALLthinToys.Rdata")
# plotTALLthinToys <- mbplot(mbTALLthinToys) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotTALLthinToys
```

### With variable importance computation

```{r, eval=FALSE}
mbTALLthinToysImp <- microbenchmark(
  randomForest::randomForest(y ~ ., TALLthinToys, mtry = 1, importance = TRUE),
  ranger::ranger(y ~ ., TALLthinToys, mtry = 1, num.threads = 1, importance = "permutation"),
  times = 25)
levels(mbTALLthinToysImp$expr) <- c("RF", "ranger")
```

```{r}
mbTALLthinToysImp
save(mbTALLthinToysImp, file = "outputs/mbTALLthinToysImp.Rdata")
# plotTALLthinToysImp <- mbplot(mbTALLthinToysImp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
# plotTALLthinToysImp
```

```{r}
mbTALLthinToys$VI <- "no VI"
mbTALLthinToysImp$VI <- "VI"
mbTALLthinToysBoth <- rbind(mbTALLthinToys, mbTALLthinToysImp)
TALLthinToysMBplot <- mbplot(mbTALLthinToysBoth)
TALLthinToysMBplot <- TALLthinToysMBplot + facet_wrap(~VI) +
  scale_fill_manual(values = viridis::viridis(4)[2:4])
TALLthinToysMBplot
```


## $n = 100000, p = 10$

```{r}
ncores <- 20
set.seed(768895)
allseeds <- round(runif(ncores, 1e5, 1e6))

alldata <- parallel::mclapply(1:ncores, function(ind) {
  set.seed(allseeds[ind])
  simu_toys(n = 100000 / ncores, p = 10)
}, mc.cores=ncores)

TALL5Toys <- do.call("rbind", alldata)
dim(TALL5Toys)
# save(TallToys, file = "data/TallToys.Rdata")
XTALL5Toys <- subset(TALL5Toys, select = -y)
mtryTALL5Toys <- floor(sqrt(ncol(XTALL5Toys)))
```

```{r, eval=FALSE}
mbTALL5Toys <- microbenchmark(
  randomForest::randomForest(y ~ ., TALL5Toys, mtry = mtryTALL5Toys),
  # ranger::ranger(y ~ ., TALL5Toys, mtry = mtryTALL5Toys, num.threads = 1),
  Rborist::Rborist(XTALL5Toys, TALL5Toys$y, predFixed = mtryTALLToys, minInfo = 0, nThread = 1),
  times = 10)
levels(mbTALL5Toys$expr) <- c("RF", "Rborist")
```

```{r}
mbTALL5Toys
save(mbTALL5Toys, file = "outputs/mbTALL5Toys.Rdata")
plotTALL5Toys <- mbplot(mbTALL5Toys) + scale_fill_manual(values = viridis::viridis(4)[c(2, 4)])
plotTALL5Toys
```

### With variable importance computation

**`ranger` ran on 10 cores in this example (too long otherwise).**

```{r, eval=FALSE}
mbTALL5ToysImp <- microbenchmark(
  randomForest::randomForest(y ~ ., TALL5Toys, mtry = mtryTALL5Toys, importance = TRUE),
  ranger::ranger(y ~ ., TALL5Toys, mtry = mtryTALL5Toys, num.threads = 10, importance = "permutation", verbose = FALSE),
  times = 10)
levels(mbTALL5ToysImp$expr) <- c("RF", "ranger")
```

```{r}
mbTALL5ToysImp
save(mbTALL5ToysImp, file = "outputs/mbTALL5ToysImp.Rdata")
plotTALL5ToysImp <- mbplot(mbTALL5ToysImp) + scale_fill_manual(values = viridis::viridis(4)[2:3])
plotTALL5ToysImp
```
